\section{LLM-Based PHP Version Migration Framework}
\label{sec:migration_framework}

We implement a controlled framework for LLM-assisted PHP migration.
It standardizes prompting, context handling, and reconstruction.
The goal is to reduce orchestration variance.
Differences should reflect model behavior, not pipeline artifacts.
Rector is used only for evaluation as the pinned contract.\cite{rector}
The migration procedure is model- and provider-agnostic.

\paragraph*{Design principles}
We enforce three constraints.
First, systems share the same degrees of freedom.
We fix prompts, chunking policy, and decoding settings where supported.
Second, extraction and reconstruction are deterministic from recorded responses.
Third, we surface failures.
Timeouts and extraction failures are reported, not repaired.
This isolates model behavior and supports fair comparison.

\subsection{Configuration and provider interface}
\label{sec:framework_config}

A centralized configuration defines model identifiers, request limits, and decoding settings where supported.
We log prompts, responses, and run metadata for audit and recomputation.

A unified provider interface normalizes authentication, request formatting, and error handling.
This keeps the migration policy consistent across systems.

\subsection{Migration policy and context management}
\label{sec:framework_chunking}

We treat context length as a fixed constraint.\cite{liu2024lost,du2025context}
Files up to 500 lines use one request.
Longer files are split to fit a bounded budget.
We use line count as a provider-agnostic proxy for request size.
Chunk boundaries depend only on the input file and pinned parameters.

We use a fixed PHP-aware boundary heuristic to reduce mid-function splits (Appendix~\ref{app:benchmark_algorithms}).
We do not use learned or adaptive chunking.

We disable overlap, retrieval augmentation, multi-pass refinement, and cross-chunk repair.
Each model runs a single-pass policy under the same constraints.

Prompts require begin and end markers.
Whole-file outputs are used directly.
Chunk outputs are concatenated in order.

\subsection{Output extraction and reconstruction}
\label{sec:framework_reconstruction}

Responses must place migrated code between markers.
The parser checks marker presence and extracts only the enclosed code.
For chunked files, we reconstruct outputs by ordered concatenation.

If extraction fails for a chunk, we insert a fixed placeholder comment that reports the failure.
We do not attempt heuristic repair.
Failures propagate to syntax checks and contract scoring.
This prevents inflated results.

We store all artifacts with raw responses and execution metadata.
This supports inspection and reproducibility.

\subsection{Illustrative migration case study}
\label{sec:framework_case_study}

Figure~\ref{fig:framework_case_study} presents a real before/after excerpt
from our stored migration artifacts for the same benchmark file.
This grounds the framework description in a verifiable transformation with
traceable file-level metrics.

\begin{figure*}[t]
\centering
\begin{subfigure}[t]{0.48\textwidth}
\centering
\caption{Legacy method excerpt}
\label{fig:framework_case_study_before}
\begin{Verbatim}[fontsize=\scriptsize,frame=single,rulecolor=\color{hdrBlue},bgcolor=rowA,framesep=3mm,breaklines=true,breakanywhere=true]
function diff($diff, $mode = 'autodetect')
{
    // Detect line breaks.
    $lnbr = "\n";
    if (strpos($diff, "\r\n") !== false) {
        $lnbr = "\r\n";
    } elseif (strpos($diff, "\r") !== false) {
        $lnbr = "\r";
    }

    // Make sure we have a line break at the EOF.
    if (substr($diff, -strlen($lnbr)) != $lnbr) {
        $diff .= $lnbr;
    }

    // ...
}
\end{Verbatim}
\end{subfigure}
\hfill
\begin{subfigure}[t]{0.48\textwidth}
\centering
\caption{Migrated method excerpt (Gemini 2.5 Pro)}
\label{fig:framework_case_study_after}
\begin{Verbatim}[fontsize=\scriptsize,frame=single,rulecolor=\color{sepLine},bgcolor=rowB,framesep=3mm,breaklines=true,breakanywhere=true]
public function diff(string $diff, string $mode = 'autodetect'): array
{
    // Detect line breaks.
    $lnbr = "\n";
    if (str_contains($diff, "\r\n")) {
        $lnbr = "\r\n";
    } elseif (str_contains($diff, "\r")) {
        $lnbr = "\r";
    }

    // Make sure we have a line break at the EOF.
    if (!str_ends_with($diff, $lnbr)) {
        $diff .= $lnbr;
    }

    // ...
}
\end{Verbatim}
\end{subfigure}
\caption{Method-level excerpt from benchmark file \texttt{062\_string.php}. The legacy version uses an untyped method and legacy string-search idioms, while the Gemini~2.5~Pro migrated version introduces explicit visibility, parameter and return types, and PHP~8 string helpers. In the full migrated file, strict types are enabled at file scope, and the method continues with modernized control flow and typed dispatch logic. The excerpt therefore illustrates contract-visible modernization while avoiding overclaiming from a partial listing alone.}
\label{fig:framework_case_study}
\end{figure*}

\subsection{Experimental orchestration}
\label{sec:framework_orchestration}

The orchestration layer applies the fixed policy, records extraction outcomes, and prepares outputs for contract evaluation.
This yields consistent experimental conditions and fully traceable runs.

