
\begin{table}[htbp]
\centering
\caption{Coverage dimensions used to characterize the triggered rule universe under the pinned contract.}
\label{tab:coverage_dimensions}
\small
\begin{tabular}{@{}l p{0.50\columnwidth}@{}}
\arrayrulecolor{hdrBlue}
\toprule[1.5pt]
\tophdr{Dimension} & \tophdr{Description} \\
\midrule[1pt]
\rowcolor{rowA}
Rule type frequency & Corpus frequency of each triggered Rector upgrade rule type. \\
\rowcolor{rowB}
PHP version mapping & Mapping triggered rules to PHP~5.x, 7.x, and 8.x milestone families. \\
\rowcolor{rowA}
Rule categories & Distribution across AST constructs such as \texttt{FuncCall}, \texttt{Array\_}, and \texttt{Class\_}. \\
\rowcolor{rowB}
Size and complexity & Relationship between LOC and rule diversity. \\
\rowcolor{rowA}
Tail coverage & Preservation of infrequent rule types during sampling. \\
\bottomrule[1.5pt]
\end{tabular}
\end{table}




\section{Pinned Contract Benchmark Construction}
\label{sec:benchmark_construction}

We construct a 100-file benchmark from WordPress~4.0 to evaluate migration under a pinned Rector contract, i.e., a fixed Rector version, ruleset, and configuration. We choose WordPress because it is large, long-lived, and exhibits substantial PHP version drift.

The benchmark is diagnostic by design. Rather than matching the natural WordPress file distribution, we optimize for coverage of the rule types triggered by the pinned contract. This improves interpretability and prevents rare but important obligations from being obscured by project-specific frequency effects. The benchmark therefore measures progress against a fixed upgrade policy, not typicality of WordPress workloads. By construction, it preserves full triggered rule-type coverage under the contract, enabling controlled and reproducible comparison of automated migration systems.

The design follows standard guidance for controlled empirical studies and reproducible benchmark construction.\cite{wohlin2012experimentation}

\paragraph*{Overview}
We construct the benchmark in three steps:
\begin{enumerate}
\item Run the pinned contract on the full corpus to obtain baseline triggers.
\item Characterize the triggered rule universe (Table~\ref{tab:coverage_dimensions}).
\item Select 100 files using size stratification while preserving all triggered rule types (Appendix~\ref{app:benchmark_algorithms}).
\end{enumerate}

We also define a separate 55-file execution slice for loadability checks. We use this slice only as a sentinel for new include-time failures under a fixed harness and interpret it only as a regression signal.



\subsection{Baseline Contract Findings}
\label{sec:benchmark_static_analysis}

We analyze the full WordPress~4.0 corpus (482 PHP files) with the reference Rector configuration, pinning \texttt{LevelSetList::UP\_TO\_PHP\_83} and tool versions to keep the contract stable across runs. Static-analysis triggers provide a scalable and consistent signal.\cite{bessey2010billion,calcagno2015moving}

We record findings as file-level rule incidence: a rule counts once per file if it triggers. We use incidence because it is stable across repeated runs of the pinned configuration, whereas in-file counts are not consistently exposed by Rector.

We also record Rector dry-run patches, which summarize the edits suggested by the pinned contract. We use these only as a proxy for residual patch volume.\cite{falleri2014fine,fluri2007change}

Across the full corpus, we observe 1{,}331 file-rule incidences spanning 48 triggered upgrade rule types. This defines the rule universe used for benchmark construction. The released 100-file benchmark preserves all 48 triggered rule types and contains 521 file-rule incidences. For the primary comparative score used later, evaluation is restricted to the version-specific \texttt{Rector\textbackslash Php*} subset, yielding 511 baseline file-rule incidences in the benchmark. The remaining 10 incidences belong to non-version-specific categories such as dead-code and code-quality rules and are excluded from the headline score.

\begin{table}[htbp]
\centering
\caption{Ranking criteria for size-stratified file selection. Exact weights are fixed a priori and given in Appendix~\ref{app:benchmark_algorithms}.}
\label{tab:selection_criteria}
\small
\begin{tabular}{@{}l p{0.50\columnwidth}@{}}
\arrayrulecolor{hdrBlue}
\toprule[1.5pt]
\tophdr{Criterion} & \tophdr{Role in file selection} \\
\midrule[1pt]
\rowcolor{rowA}
Rule diversity & Prefer files triggering many distinct rule types. \\
\rowcolor{rowB}
Version change density & Reward stronger evidence of version-related changes. \\
\rowcolor{rowA}
Size suitability & Favor 100 to 2000 LOC and penalize very large files. \\
\rowcolor{rowB}
PHP family breadth & Prefer files spanning multiple PHP milestone families. \\
\rowcolor{rowA}
Key patterns & Add weight for migration-relevant constructs. \\
\bottomrule[1.5pt]
\end{tabular}
\end{table}

\subsection{Coverage-Preserving Selection}
\label{sec:benchmark_selection}

We summarize baseline triggers to characterize rule frequency, milestone coverage, and size effects. Because rare rule types are easy to lose under uniform sampling, we enforce full triggered rule-type coverage during selection.

Selection proceeds in two stages. We first stratify files by size and rank them using the criteria in Table~\ref{tab:selection_criteria}. We then enforce full triggered rule-type coverage and trim the set to exactly 100 files while preserving that coverage. The procedure is deterministic and fixed before any LLM experiments.

\begin{table*}[t]
\centering

\begin{minipage}[t]{0.46\textwidth}
\centering
\captionof{table}{Target size distribution for stratified initialization. Realized shares may differ after coverage enforcement.}
\label{tab:size_distribution}
\small
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{1.18}
\begin{tabular}{@{}l c c@{}}
\arrayrulecolor{hdrBlue}
\toprule[1.5pt]
\tophdr{Category} & \tophdr{LOC range} & \tophdr{Share} \\
\midrule[1pt]
\rowcolor{rowA}
Small & 1--200 & 35\% \\
\rowcolor{rowB}
Medium & 201--500 & 30\% \\
\rowcolor{rowA}
Large & 501--1000 & 25\% \\
\rowcolor{rowB}
Extra large & 1001+ & 10\% \\
\bottomrule[1.5pt]
\end{tabular}
\end{minipage}
\hfill
\begin{minipage}[t]{0.50\textwidth}
\centering
\captionof{table}{File counts and average migration complexity by file size in the released benchmark, reported across the four benchmark size categories.}
\label{tab:migration_complexity}
\small
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{1.18}
\begin{tabular}{@{}l c c c@{}}
\arrayrulecolor{hdrBlue}
\toprule[1.5pt]
\tophdr{Category} & \tophdr{Files} & \tophdr{Rules/File} & \tophdr{Milestones/File} \\
\midrule[1pt]
\rowcolor{rowA}
Small & 31 & 3.2 & 2.9 \\
\rowcolor{rowB}
Medium & 31 & 5.4 & 4.8 \\
\rowcolor{rowA}
Large & 26 & 5.7 & 5.0 \\
\rowcolor{rowB}
Extra large & 12 & 8.9 & 6.2 \\
\bottomrule[1.5pt]
\end{tabular}
\end{minipage}

\end{table*}

\subsection{Benchmark Integrity}
\label{sec:benchmark_validation}

All selected files run successfully under the pinned contract. The benchmark preserves all 48 triggered upgrade rule types and contains 521 file-rule incidences spanning PHP~5.2 to 8.3 milestones. Larger files trigger more rule types and span more milestones (Table~\ref{tab:migration_complexity}), consistent with prior links between structural complexity and transformation diversity.\cite{chidamber1994metrics,mccabe1976complexity}. Here, Rules/File is the average number of triggered rule types per file and Milestones/File is the average number of distinct PHP version milestones represented per file in (Table~\ref{tab:migration_complexity}).

Because rule coverage is the hard constraint, the realized size mix differs slightly from the target distribution in Table~\ref{tab:size_distribution}.

We also define a 55-file loadability slice. On this slice, we report only new failures (original pass, migrated fail) under a fixed harness and do not interpret absolute pass rates as behavioral correctness.