\section{Pinned Contract Evaluation}
\label{sec:rector_eval}

\subsection{Setup}
\label{sec:pce_objective_instrument}

Pinned Contract Evaluation (PCE) measures migration progress under a fixed upgrade policy, not functional correctness. We instantiate the policy as a pinned Rector configuration with fixed version, ruleset, and parameters.\cite{rector} We call this configuration the \emph{migration contract}.

We run the contract on each original benchmark file and on its migrated output. For file $i$, the original run yields the set of triggered upgrade rule types, which defines that file's obligations. For analyzable migrated files, the post-migration run identifies discharged obligations and newly introduced rule types.

If Rector cannot analyze a migrated file, that file contributes zero discharged obligations to the primary all-files aggregate, while its original obligations remain in the denominator. Post-migration trigger-based quantities are then undefined; analyzable coverage is reported separately.

We score only \texttt{Rector\textbackslash Php*} rules. To contextualize contract outcomes, we also report syntax, preservation, loadability, and PHPCompatibility diagnostics.\cite{phpcompat}

\subsection{Signals}
\label{sec:pce_primary_scores}

PCE reports two signals.

\textbf{(1) Obligation discharge (primary).}
This measures compliance breadth. The unit is a file-level rule-type incidence, so each rule type counts at most once per file.

\textbf{(2) Patch volume closure (secondary).}
This measures how much Rector dry-run patch volume remains after migration. We use it only as a residual-work proxy, not as a correctness or effort measure.

% =========================
% Per file metrics table
% =========================
\begin{table}[t]
\centering
\caption{Per-file metrics under the pinned contract.}
\label{tab:per_file_eval_metrics}
\small
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{1.12}
\begin{tabularx}{\columnwidth}{@{}>{\raggedright\arraybackslash}p{0.36\columnwidth} >{\raggedright\arraybackslash}X@{}}
\arrayrulecolor{hdrBlue}
\toprule[1.5pt]
\tophdr{Metric} & \tophdr{Definition} \\
\midrule[1pt]
\rowcolor{rowA}
Original triggers ($\mathcal{O}_i$, $O_i$) &
Rule types triggered in file $i$ before migration. $O_i=|\mathcal{O}_i|$. \\
\rowcolor{rowB}
Post triggers ($\mathcal{R}_i$, $R_i$) &
Rule types triggered in file $i$ after migration. Defined only for analyzable migrated files. $R_i=|\mathcal{R}_i|$. \\
\rowcolor{rowA}
Discharged / introduced ($S_i$, $I_i$) &
For analyzable migrated files,
$S_i=|\mathcal{O}_i\setminus\mathcal{R}_i|$ and
$I_i=|\mathcal{R}_i\setminus\mathcal{O}_i|$. \\
\rowcolor{rowB}
All-files discharge ($S_i^*$) &
$S_i^*=S_i$ if the migrated file is analyzable, else $S_i^*=0$. \\
\rowcolor{rowA}
Discharge rate ($\rho_i$) &
For analyzable migrated files,
$\rho_i=\frac{S_i}{O_i}\times 100$. \\
\rowcolor{rowB}
Patch volume ($D_i$) &
Changed-line count in the Rector dry-run patch (\texttt{diff\_line\_count}). \\
\rowcolor{rowA}
Patch closure (\%) &
Closure relative to $D_i^{\mathrm{orig}}$ using WDC and MFDC. \\
\bottomrule[1.5pt]
\end{tabularx}
\end{table}

% =========================
% Outcome matrices table
% =========================
\begin{table}[t]
\centering
\caption[Outcome matrices for syntax and loadability]{Outcome matrices for syntax lint and the isolated loadability tripwire. Loadability is regression-oriented: orig.\ pass $\rightarrow$ migr.\ fail.}
\label{tab:outcome_matrices}
\scriptsize
\setlength{\tabcolsep}{3pt}
\renewcommand{\arraystretch}{1.05}
\begin{subtable}[t]{0.46\columnwidth}
\centering
\caption{Syntax}
\label{tab:syntax_validation_outcomes}
\begin{tabular}{@{}lcc@{}}
\arrayrulecolor{hdrBlue}
\toprule[1.2pt]
\tophdr{Outcome} & \tophdr{Orig.} & \tophdr{Migr.} \\
\midrule[0.8pt]
\rowcolor{rowA}
Both valid  & Pass & Pass \\
\rowcolor{rowB}
Fixed error & Fail & Pass \\
\rowcolor{rowA}
New error   & Pass & Fail \\
\rowcolor{rowB}
Both error  & Fail & Fail \\
\bottomrule[1.2pt]
\end{tabular}
\end{subtable}
\hspace{6pt}
\begin{subtable}[t]{0.46\columnwidth}
\centering
\caption{Loadability}
\label{tab:runtime_validation_outcomes}
\begin{tabular}{@{}lcc@{}}
\arrayrulecolor{hdrBlue}
\toprule[1.2pt]
\tophdr{Outcome} & \tophdr{Orig.} & \tophdr{Migr.} \\
\midrule[0.8pt]
\rowcolor{rowA}
Both pass     & Pass & Pass \\
\rowcolor{rowB}
Fixed failure & Fail & Pass \\
\rowcolor{rowA}
New failure   & Pass & Fail \\
\rowcolor{rowB}
Both fail     & Fail & Fail \\
\bottomrule[1.2pt]
\end{tabular}
\end{subtable}
\end{table}

% =========================
% Structural diagnostics table
% =========================
\begin{table}[t]
\centering
\caption{Structural preservation signals.}
\label{tab:structural_completeness_signals}
\small
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{1.10}
\begin{tabularx}{\columnwidth}{@{}l X@{}}
\arrayrulecolor{hdrBlue}
\toprule[1.5pt]
\tophdr{Signal} & \tophdr{Purpose} \\
\midrule[1pt]
\rowcolor{rowA}
Token dist.\ sim. & Token-type frequency similarity excluding trivia. \\
\rowcolor{rowB}
Token seq.\ sim.  & Order-sensitive similarity on a normalized token stream. \\
\rowcolor{rowA}
Decl.\ overlap    & Set overlap of namespaces, classes, functions, and methods. \\
\rowcolor{rowB}
Line preservation & Code-line retention excluding blank and comment lines. \\
\rowcolor{rowA}
Body preservation & Body-token retention for matched declarations. \\
\rowcolor{rowB}
Signature stability & Parameter and modifier consistency for matched declarations. \\
\rowcolor{rowA}
Empty body rate   & Fraction of matched bodies that are near-empty. \\
\rowcolor{rowB}
Trivial stub rate & Fraction of matched bodies with shallow stub patterns. \\
\midrule[0.6pt]
\multicolumn{2}{@{}p{\columnwidth}@{}}{\footnotesize\emph{Note:} Body and stub signals apply only when bodies exist; otherwise they are N/A.} \\
\bottomrule[1.5pt]
\end{tabularx}
\end{table}

\subsubsection{Breadth: obligation discharge}
\label{sec:pce_breadth}

For file $i$, let $\mathcal{O}_i$ be the set of rule types triggered on the original file under the contract, and let $\mathcal{R}_i$ be the set triggered on the migrated file when that file is analyzable. Let $O_i=|\mathcal{O}_i|$ and $R_i=|\mathcal{R}_i|$.

For analyzable migrated files,
\[
\begin{aligned}
S_i &= |\mathcal{O}_i \setminus \mathcal{R}_i|
\quad \text{(discharged types)}, \\
I_i &= |\mathcal{R}_i \setminus \mathcal{O}_i|
\quad \text{(introduced types)}.
\end{aligned}
\]

The per-file discharge rate is
\[
\rho_i = \frac{S_i}{O_i}\times 100.
\]

For the primary all-files aggregate, we define
\[
S_i^*=
\begin{cases}
S_i, & \text{if the migrated file is analyzable,}\\
0, & \text{otherwise.}
\end{cases}
\]

All benchmark files satisfy $O_i>0$ by construction. We report $I_i$ as a contract-visible regression signal.

\subsubsection{Secondary proxy: patch volume closure}
\label{sec:pce_depth}

Let $D_i$ be Rector's dry-run changed-line count for file $i$ on the migrated output, and let $D_i^{\mathrm{orig}}$ be the corresponding quantity on the original file under the same contract. We summarize patch-volume reduction in two ways: workload-weighted closure (WDC), which emphasizes high-volume files, and mean file closure (MFDC), which weights files uniformly. Files with missing or unreadable values are excluded from these aggregates.

\providecommand{\WDC}{\textnormal{WDC}}
\providecommand{\MFDC}{\mathrm{MFDC}}
{\footnotesize
\begin{align}
\WDC(m)
&= \left(1-\frac{\sum_i D_i^{m}}{\sum_i D_i^{\mathrm{orig}}}\right)\cdot 100,\\
\MFDC(m)
&= \frac{1}{N}\sum_i c_i,\\[-2pt]
c_i
&=
\begin{aligned}[t]
\left(1-\frac{D_i^{m}}{D_i^{\mathrm{orig}}}\right)\cdot 100 \;& (D_i^{\mathrm{orig}}>0)\\
100 \;& (D_i^{\mathrm{orig}}=0,\, D_i^{m}=0)\\
0 \;& (D_i^{\mathrm{orig}}=0,\, D_i^{m}>0)\;.
\end{aligned}
\end{align}
}
We treat patch closure only as supporting context, since stylistic rewrites and diff shaping can inflate it.

\subsection{Reporting}
\label{sec:pce_interpretation}

For each file we record $O_i$; for analyzable migrated files we additionally record $R_i$, $S_i$, $I_i$, and $\rho_i$. We also record $D_i$ and the diagnostic metadata in Table~\ref{tab:per_file_eval_metrics}.

Our primary comparison is the all-files weighted discharge rate:
\[
\rho_w^{\mathrm{all}} =
\frac{\sum_{i=1}^{100} S_i^*}{\sum_{i=1}^{100} O_i}\times 100.
\]

This is the fraction of baseline obligations discharged across the benchmark. Because all models are scored against the same denominator, $\rho_w^{\mathrm{all}}$ supports direct comparison even when analyzable coverage differs.

We report analyzable file counts separately. In our benchmark they are: Rector 100, Claude 97, Gemini Flash 91, Gemini Pro 97, GPT 5 Codex 88, and Llama 95.

On analyzable migrated files, we additionally report mean $\rho_i$, post triggers $R_i$, introduced triggers $I_i$, contract-clean counts, low-compliance counts, and size/family breakdowns:
\begin{align}
N_{\mathrm{contract\ clean}} &= |\{ i \mid R_i=0 \}|,\\
N_{\mathrm{low\ compliance}} &= |\{ i \mid \rho_i<50 \}|.
\end{align}

PCE should be interpreted jointly with validity, preservation, and loadability diagnostics. In particular, $I_i$ indicates a contract regression under the pinned policy, not a behavioral regression.

\subsection{Diagnostics}
\label{sec:pce_validity_diagnostics}

Contract scores can be misleading when outputs contain omissions, degenerate rewrites, syntax errors, or include-time failures. We therefore report a fixed diagnostic suite for every output. These checks provide validity and regression evidence, but do not establish functional equivalence.

\paragraph*{Diagnostic tiers}\
We report
(i) syntax validation via \texttt{php -l} (PHP~8.3),
(ii) structural preservation signals (Table~\ref{tab:structural_completeness_signals}),
(iii) contract metrics under Rector,
(iv) PHPCompatibility results, and
(v) a loadability sentinel (Section~\ref{sec:pce_loadability}).
Outcome definitions appear in Table~\ref{tab:outcome_matrices}. Metrics that require parsing are N/A when \texttt{php -l} fails.

\subsection{Isolated loadability sentinel}
\label{sec:pce_loadability}

We run a loadability sentinel on a fixed slice ($N_{\mathrm{rt}}=55$). Each file is loaded once via \texttt{require\_once} in a minimal WordPress stub harness. Parse errors, fatal errors, and uncaught exceptions count as failures. We interpret this tier only as a regression signal, with regression defined as orig.\ pass and migr.\ fail.

\subsection{Cross-instrument triangulation with PHPCompatibility}
\label{sec:pce_phpcompat}

We triangulate Rector-based scores with PHPCompatibility.\cite{phpcompat} For each output set we run PHPCS with \texttt{--standard=PHPCompatibility} and \texttt{--runtime-set testVersion 8.3}, parse the JSON reports, and compute issue reduction:
\[
\text{IssueReduction}(\%)=
\frac{\text{Issues}_{\mathrm{orig}}-\text{Issues}_{\mathrm{model}}}
{\text{Issues}_{\mathrm{orig}}}\times 100.
\]

Because PHPCompatibility uses a different rule set and granularity than Rector, agreement indicates consistent movement across instruments, whereas divergence reflects policy differences.

\subsection{Contract-aligned reference baseline}
\label{sec:pce_baseline}

We include a contract-aligned reference baseline, \emph{Rector applied}. We apply the pinned ruleset to each file and then rerun the same contract on the rewritten output.

This baseline is not necessarily trigger-free: Rector rules are conservative and pattern-limited. It therefore serves as a practical ceiling under the same policy and scoring protocol.